The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-03-25 index.qmd
woohoo got this working with {rbbt}

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
format:
  html:
    code-tools: false
    toc: false
---

>>>>

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
format:
  html:
    code-tools: false
    toc: false
---

### 2023-03-25 manuscript/manuscript.qmd
woohoo got this working with {rbbt}

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
bibliography: references.bib
link-citations: true
format: 
  html:
    toc: true
  pdf: default
  docx: default
language: 
  title-block-published: "Latest version"
---

Lorem ipsum dolor sit amet, consectetur adipisicing elit [@Mayer:2010], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
bibliography: references.bib
link-citations: true
format: 
  html:
    toc: true
  pdf: default
  docx: default
language: 
  title-block-published: "Latest version"
---

Lorem ipsum dolor sit amet, consectetur adipisicing elit [@ChaudhryHeiss:2022], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
